---
title: "Linear Regression Project"
author: "Salvatore Matteis, Zain ElHashemite, Matthew Vasquez"
date: "2023-04-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Trying to predict "CELZ"
## Using "ATAT", "SCLX", "MDB", "AMZN", "BA"

# 1. Create a function that runs a linear regression model on a data set with an unspecified number of predictors and outputs both the coefficients and their associated p-vals.

```{r}
my_lm <- function(data) {
  # extract the response variable (last column) and the predictors (all other columns)
  y <- data[,ncol(data)]
  X <- data[,1:(ncol(data)-1)]
  X = cbind(rep(1, dim(X)[1]), X)

  # calculate the coefficients and standard errors using the matrix algebra formula for OLS
  beta_hat <- solve(t(X) %*% X) %*% t(X) %*% y
  n <- length(y)
  k <- ncol(X)
  SSE <- sum((y - X %*% beta_hat)^2)
  sigma_hat_sq <- SSE/(n - k)
  C_inv <- solve(t(X) %*% X)
  se <- sqrt(sigma_hat_sq * diag(C_inv))
  t_stats <- beta_hat/se
  p_vals <- 2*pt(-abs(t_stats), df = n - k)
  
  # return a list of the coefficients, standard errors, and their associated p-vals
  return(list(beta = beta_hat, se = se, p.val = p_vals))
}

```

#Test
```{r}
# create a matrix with some fake data
data <- matrix(rnorm(90), ncol = 6)
colnames(data) <- c("ATAT", "SCLX", "MDB", "AMZN", "BA", "CELZ")
y <- data[,ncol(data)]
X <- data[,1:(ncol(data)-1)]
df = data.frame(data)
# run the my_lm function on the fake data
my_lm(data)

```

#2. Choose either Forward or Backward subset selection and choose either adjusted R-squared or validation set, and then stick with this choice for the remaining problems.

```{r}
library(quantmod)

# Set seed 
CWID = 20010286
seed = CWID %% 10000
set.seed(seed)

# Define the ticker symbols and time frame
tickers <- c("CELZ", "ATAT", "SCLX", "MDB", "AMZN", "BA")
start_date <- as.Date("2023-01-21")
end_date <- as.Date("2023-04-21")

# Download the stock data using quantmod
getSymbols(tickers, from = start_date, to = end_date)

# Combine the adjusted close prices into a single data frame
stock_prices <- data.frame(CELZ = as.numeric(CELZ$CELZ.Adjusted),
                           ATAT = as.numeric(ATAT$ATAT.Adjusted),
                           SCLX = as.numeric(SCLX$SCLX.Adjusted),
                           MDB = as.numeric(MDB$MDB.Adjusted),
                           AMZN = as.numeric(AMZN$AMZN.Adjusted),
                           BA = as.numeric(BA$BA.Adjusted))

# Define the predictor and response variables
response_var <- "CELZ"
predictor_vars <- c("ATAT", "SCLX", "MDB", "AMZN", "BA")

# Set up the forward subset selection function with adjusted R-squared
forward_subset_selection_adjustedR2_custom <- function(data, response_var, predictor_vars){
  
  # Initialize an empty set of selected predictors
  selected_predictors <- c()
  
  # Initialize the best R-squared value as 0
  best_r2 <- 0
  
  # Loop through all possible predictors
  for (i in seq_along(predictor_vars)) {
    
    # Add the next predictor to the set of selected predictors
    selected_predictors <- c(selected_predictors, predictor_vars[i])
    
    # Fit a linear model using the selected predictors and calculate the adjusted R-squared using my_lm function
    y <- data[, response_var]
    X <- as.matrix(data[, selected_predictors])
    
    
    print(X)
    print(y)
    
    
    fit <- my_lm(cbind(X, y))
    y_hat <- X %*% fit$beta
    SSE <- sum((y - y_hat)^2)
    SST <- sum((y - mean(y))^2)
    R2 <- 1 - SSE/SST
    r2_adj <- 1 - (1 - R2)*(nrow(data) - 1)/(nrow(data) - length(selected_predictors) - 1)
    
    # If the adjusted R-squared is better than the current best, update the best R-squared and the best set of selected predictors
    if (r2_adj > best_r2) {
      best_r2 <- r2_adj
      best_predictors <- selected_predictors
    }
    
  }
  
  # Return the best set of selected predictors
  return(best_predictors)
  
}

# Run the forward subset selection function
selected_predictors <- forward_subset_selection_adjustedR2_custom(data = stock_prices, response_var = response_var, predictor_vars = predictor_vars)

# Print the selected predictors
print(selected_predictors)


```

#3
```{r}
# Subset the stock_prices data frame to include only the first two months of data
stock_prices_first_two_months <- stock_prices[1:41, ]

# Select the predictor variables B through F and the response variable A
response_var <- "CELZ"
predictor_vars <- c("ATAT", "SCLX", "MDB", "AMZN", "BA")

# Use the forward subset selection function to determine the best set of selected predictors based on the adjusted R-squared value
selected_predictors <- forward_subset_selection_adjustedR2_custom(data = stock_prices_first_two_months, response_var = response_var, predictor_vars = predictor_vars)

# Print the selected predictors
print(selected_predictors)

# Fit a linear regression model using the my_lm function and the selected predictors for the first two months of data
y <- stock_prices_first_two_months[, response_var]
X <- as.matrix(stock_prices_first_two_months[, selected_predictors])
fit <- my_lm(cbind(X, y))

# Calculate the R-squared value for the first two months of data
y_hat <- X %*% fit$beta
SSE <- sum((y - y_hat)^2)
SST <- sum((y - mean(y))^2)
R2 <- 1 - SSE/SST
print(paste0("R-squared value for the first two months of data: ", round(R2, 4)))

# Calculate the predicted values for the third month using the fitted model and the best set of selected predictors
stock_prices_third_month <- stock_prices[42, ]
y_pred <- as.numeric(stock_prices_third_month[response_var])
X_pred <- as.matrix(stock_prices_third_month[selected_predictors])
y_hat_pred <- X_pred %*% fit$beta

# Calculate the mean squared error for the third month
MSE <- mean((y_pred - y_hat_pred)^2)
print(paste0("Mean squared error for the third month: ", round(MSE, 4)))



```
#4 Repeat step 3, but also include the squares of the stock prices (so you will have 10 predictors, e.g. B, B^2, C, C^2, etc.).

```{r}


prices = c(ATAT$ATAT.Adjusted, SCLX$SCLX.Adjusted, MDB$MDB.Adjusted, AMZN$AMZN.Adjusted, BA$BA.Adjusted)

prices_sq = c(ATAT$ATAT.Adjusted^2, SCLX$SCLX.Adjusted^2, MDB$MDB.Adjusted^2, AMZN$AMZN.Adjusted^2, BA$BA.Adjusted^2)

data = data.frame(prices, prices_sq)
data


```
