---
output: pdf_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

# QF112. Homework #1.

## `r format(Sys.time(), "%Y-%m-%d")`

I pledge on my honor that I have not given or received any unauthorized assistance on this assignment/examination. I further pledge that I have not copied any material from a book, article, the Internet or any other source except where I have expressly cited the source.

By filling out the following fields, you are signing this pledge. No assignment will get credit without being pledged.

Name: Zain ElHashemite

CWID: 20010286

Date: 1/21/2023

```{r}
CWID = 20010286 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

# Question 1

Use R to calculate the square root of 30

```{r}
sqrt30 = sqrt(30)
print(sqrt30)
```

# Question 2

What is 34.6 multiplied by 23.5

```{r}
prod = 34.6*23.5
print(prod)
```

# Question 3

Create a vector of the first 10 elements of the Fibonacci sequence

```{r}
vector = c(0,1,1,2,3,5,8,13,21,34)
print(vector)
```

# Question 4

Create a data frame consisting of the first 10 elements of the Fibonacci sequence as well as their index in the sequence. Name the columns appropriately.

```{r}

index = c(1:10)
frame1 = data.frame(index,vector)
colnames(frame1)[1] = "Index"
colnames(frame1)[2] = "Fibonacci Value"
frame1

```
