---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #5.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name: Zain ElHashemite

CWID: 20010286

Date: 2/17/2023




```{r}
CWID = 20010286 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
library(quantmod)
getSymbols("AAPL", src = "yahoo", from = "2022-01-01", to = "2023-01-01")
getSymbols("ADP", src = "yahoo", from = "2022-01-01", to = "2023-01-01")

write.csv(as.data.frame(AAPL), "AAPL.csv")
write.csv(as.data.frame(ADP), "ADP.csv")

frame1 = data.frame(AAPL)
frame2 = data.frame(ADP)
```

# Question 1 

For this problem, you will be using your previous data set of the two assets that you downloaded.

## a)

For the first asset, determine the 60%, 90%, and 95% confidence intervals for the population mean of the adjusted close prices.

```{r}

xbar = mean(AAPL$AAPL.Adjusted)
sd = sd(AAPL$AAPL.Adjusted)

a = .4
a1 = .1
a2 = .05

n = length(AAPL$AAPL.Adjusted)

conf60 = qnorm(1-(a/2)) * (sd/(sqrt(n)))
bound = c(xbar - conf60, xbar+conf60)
bound

#[153.4652, 154.8279]

conf90 = qnorm(1-(a1/2)) * (sd/(sqrt(n)))
bound1 = c(xbar - conf90, xbar+conf90)
bound1

#[152.8149, 155.4782]

conf95 = qnorm(1-(a2/2)) * (sd/(sqrt(n)))
bound2 = c(xbar - conf95, xbar+conf95)
bound2

#[152.5598, 155.7333]




```

## b)


For the first asset, restrict your data set to just the most recent two weeks.  Use only this data to determine the 60%, 90%, and 95% confidence intervals for the population mean of the adjusted close prices.

```{r}
library(quantmod)
getSymbols("AAPL", src = "yahoo", from = "2022-02-08", to = "2023-02-22")

write.csv(as.data.frame(AAPL), "AAPL2.csv")

frame1 = data.frame(AAPL)



xbar = mean(AAPL$AAPL.Adjusted)
sd = sd(AAPL$AAPL.Adjusted)

a = .4
a1 = .1
a2 = .05

n = length(AAPL$AAPL.Adjusted)

conf60 = qt(1-(a/2), n - 1) * (sd/(sqrt(n)))
bound = c(xbar - conf60, xbar+conf60)
bound
#[150.4840, 151.7827]


conf90 = qt(1-(a1/2), n - 1) * (sd/(sqrt(n)))
bound1 = c(xbar - conf90, xbar+conf90)
bound1
#[149.8617, 152.4049]

conf95 = qt(1-(a2/2), n - 1) * (sd/(sqrt(n)))
bound2 = c(xbar - conf95, xbar+conf95)
bound2
#[149.6165, 152.6502]



```

## c)

For the second asset, determine the 60%, 90%, and 95% confidence intervals for the population variance.

```{r}
library(quantmod)
getSymbols("ADP", src = "yahoo", from = "2022-01-01", to = "2023-01-01")
write.csv(as.data.frame(ADP), "ADP.csv")
frame2 = data.frame(ADP)

n = length(ADP$ADP.Adjusted)
xbar = mean(ADP$ADP.Adjusted)

sd = sd(ADP$ADP.Adjusted)

a = .4
a1 = .1
a2 = .05

conf60 = qnorm(1-(a/2)) * (sd/sqrt(n))
bound = c(xbar - conf60, xbar+conf60)
bound
#[225.4994, 227.4794]

conf90 = qnorm(1-(a1/2)) * (sd/sqrt(n))
bound1 = c(xbar - conf90, xbar+conf90)
bound1
#[224.5545, 228.4242]

conf95 = qnorm(1-(a2/2)) * (sd/sqrt(n))
bound2 = c(xbar - conf95, xbar+conf95)
bound2
#[224.1838, 228.7949]

```

## d)

After converting your second asset to the log returns (if you had this wrong on a previous homework, please reach out to see how to fix it), determine the confidence intervals of the population variance of these log-returns at the 60%, 90%, and 95% levels.

```{r}
ADPL = as.vector(diff(log(ADP$ADP.Adjusted))[-1])

xbar = mean(ADPL)
xbar

n = length(ADPL)

sd = sd(ADPL)

a = 0.4
a1=0.1
a2=0.05

conf60 = qnorm(1-(a/2)) * (sd/sqrt(n))
bound = c(xbar - conf60, xbar+conf60)
bound
#[-0.0009624720,  0.0009426681]

conf90 = qnorm(1-(a1/2)) * (sd/sqrt(n))
bound1 = c(xbar - conf90, xbar+conf90)
bound1
#[-0.001871592,  0.001851789]

conf95 = qnorm(1-(a2/2)) * (sd/sqrt(n))
bound2 = c(xbar - conf95, xbar+conf95)
bound2
#[-0.002228243,  0.002208439]
```

# Question 2 (Adapted from Stinerock)

A study of 450 families found that 212 out of the had to cut back recently on the purchase of big-ticket items over the past 6 months.

## a)

What is the 90% confidence interval estimate of the population proportion $p$ of the households that are cutting back?

```{r}

n = 450
p_hat = 212/n
p_hat

sqrt_p = 1.645*sqrt((p_hat*(1-p_hat))/n)
sqrt_p

p_hat + sqrt_p
p_hat - sqrt_p 
#[0.4324029, 0.5098194]

```

## b)

What sample size would you recommend to achieve a margin of error of .03?

```{r}

p_hat = 212/450
moe = 0.03
n = ((1.645)^2) * (p_hat*(1-p_hat))/((moe)^2)
n

#to achieve a margin of error of 0.03 a sample size of 749 should be used.


```

## c)

How large a sample size would be required to achieve a 99% confidence interval estimate of $p$ with a margin of error of .03?
```{r}

p_hat = 212/450

moe = 0.03
n = ((2.575)^2) * (p_hat*(1-p_hat))/((moe)^2)
n

#to achieve a 99% confidence interval estimate with a margin of error of 0.03 a sample size of 1836 should be used.

```

## d)

How large a sample size would be required to achieve a 99% confidence interval estimate of $p$ with a margin of error of .025?

```{r}

p_hat = 212/450

moe = 0.025

n = ((2.575)^2) * (p_hat*(1-p_hat)) / ((moe)^2)
n

#to achieve a 99% confidence interval estimate with a margin of error of 0.025 a sample size of 2643 should be used.

```

# Question 3 (Taken from Mathematical Statistics and Data Analysis by John Rice)

Answer whether the following are true or false and why.  Note that the why part is also very important

# a)

The center of a 95% confidence interval for the population mean is a random variable

  - True, the sample mean is a random variable because the sample mean will vary for the samples across a population. 

# b) 

A 95% confidence interval for $\mu$ contains the sample mean with probability .95

  - False, the sample mean will always be contained within a confidence interval for the population.

# c)

A 95% confidence interval contains 95% of the population
  
  - False, a 95% confidence interval does not contain 95% of the population. It is a set of values which can be 95% certain to contain the population mean.

# d)

Out of one hunderd 95% confidence intervals for $\mu$, 95 will contain $\mu$.

  - False, a 95% confidence interval is a 95% chance that the population mean will be contained within the set of values, it does not mean that out of 100 95% confidence intervals, 95/100 of them will contain mu.


