---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #3.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name: Zain ElHashemite

CWID: 20010286

Date: 2/9/2023




```{r}
CWID = 20010286 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
# my response
```

# Question 1 (adapted from Stinerock: Statistics with R)

In 2013, the average level of debt from graduating students was 27,000 dollars.  We will assume this as the population mean with a standard deviation of 4500.  If we take a sample of 121 graduates, answer the following questions.

## a)

What is the probability that $\bar{x}$ will fall within 500 dollars of the population mean?
```{r}
#pop mean = 27000
#pop sd = 4500
#sample = 121

se = 4500/(sqrt(121))

left.a = (27000-27000-500)/se
right.a = (27000-27000+500)/se
left1.a = pnorm(left.a)
right1.a = pnorm(right.a)

prob.a = right1.a-left1.a
prob.a #0.7783764 or 77.83%



```

## b)

What is the probability that $\bar{x}$ will fall within 250 dollars of the population mean?
```{r}
#pop mean = 27000
#pop sd = 4500
#sample = 121

se = 4500/(sqrt(121))

left.b = (27000-27000-250)/se
right.b = (27000-27000+250)/se

left1.b = pnorm(left.b)
right1.b = pnorm(right.b)

prob.b = right1.b-left1.b
prob.b #0.458874 or 45.88%



```

# Question 2 (adapted from Stinerock: Statistics with R)

If we assume that the percentage of people in the world who are left handed is 12\%, answer the following

## a) 
 If a sample of $n=400$ people is chosen at random, what is the probability that $\bar{p}$ is within .02 of $p$?
 
```{r}
#prob(0.10 < p < 0.14)

(pnorm(0.14,0.12,sqrt((0.12*.88)/400))) - (pnorm(0.10,0.12,sqrt((0.12*.88)/400)))

```
 
## b)

Answer the same question as in part a) but this time, assume that $n=800$.

```{r}
#prob(0.10 < p < 0.14)

(pnorm(0.14,0.12,sqrt((0.12*.88)/800))) - (pnorm(0.10,0.12,sqrt((0.12*.88)/800)))

```

# Question 3

Load in the data set that you created for homework 2 (consisting of the adjusted close prices for one year for two assets, which we'll arbitrarily label asset A and asset B).  we will be treating these data sets as the true population, so this is a finite population.  As a result, you will be sampling without replacement for this problem.  Answer the following:

```{r}
library(quantmod)
getSymbols("AAPL", src = "yahoo", from = "2022-01-01", to = "2023-01-01")
getSymbols("ADP", src = "yahoo", from = "2022-01-01", to = "2023-01-01")

write.csv(as.data.frame(AAPL), "AAPL.csv")
write.csv(as.data.frame(ADP), "ADP.csv")

frame1 = data.frame(AAPL)
frame2 = data.frame(ADP)

```


## a)

Assuming that your data set is the true population, for asset A, determine the two population parameters, $\mu_A$ and $\sigma_A$.
```{r}

mu_A = mean(AAPL$AAPL.Adjusted)
sigma_A = ((sqrt(length(AAPL$AAPL.Adjusted)-1))/sqrt(length(AAPL$AAPL.Adjusted))*sd(AAPL$AAPL.Adjusted))


mu_A
sigma_A
```

## b)

If you were to take a sample of $n=40$ values from this data set, what is the probability that $\bar{x_A}$ would be within 1 dollar of the population mean?

```{r}

pnorm(155.1466, 154.1466, (12.82598/sqrt(40))) - pnorm(153.1466, 154.1466,(12.82598/sqrt(40)))

```


## c)

Generate 1000 samples of size $n=40$ from your data.  What percentage of these sample means are within 1 dollar of the population mean?  Does your answer agree with what you determined in part b)?  Why or why not?

```{r}

samples=replicate(1000,sample(AAPL$AAPL.Adjusted,40))
muS = colMeans((samples))
(length(which(muS>mu_A-1 & muS<mu_A+1))/length(muS)) *100

#Yes this answer agrees with what was determined in part B as the values are fairly close to each other. However if another test was run with a larger sample set then we could get closer to the value determined in part B.



```

## d)

Do part c) again, but this time use 10000 samples.

```{r}
samplesD=replicate(10000,sample(AAPL$AAPL.Adjusted,40))
muS1 = colMeans((samplesD))
(length(which(muS1>mu_A-1 & muS1<mu_A+1))/length(muS1)) 


```


## e)

Using asset B, modify your data to determine when the stock increases in value.  To do this, use the sign and diff functions, which will result in a vector of $N-1$ values  These will be -1 for a decrease, 0 for the stock staying the same, and 1 for an increase.  Treat this new vector as your new population.  Let $p_B$ be the percentage of days in which the stock increases in value.

```{r}

rtn = diff(log(AAPL$AAPL.Adjusted))[-1]


pos = length(rtn[rtn>0])

(pos/length(AAPL$AAPL.Adjusted))



```

## f)
If you were to take a sample of $n=50$ values from this data set, what is the probability that $\bar{p_B}$ would be within 2 percent of the population proportion?

```{r}

n=50
pnorm(.486, .466, (sqrt((.466)*(1-.466)))/sqrt(n)) - pnorm(.446, .466, (sqrt((.466)*(1-.466)))/sqrt(n))



0
```

## g)
Generate 1000 samples of size $n=50$ from your data.  What percentage of these sample proportions are within 2 percent of the population percentage?  Does your answer agree with what you determined in part f)?  Why or why not?
```{r}

mydata = data.frame(ADP)
sam = replicate(1000,sample(mydata$ADP.Adjusted,50))
sign = sign(diff(sam,log=1, differences =1))
sign[sign==-1] = 
sum_ = (colSums(sign))
length(subset(sum_,(24.3)>sum_ & sum_>(20.3)))/1000

# No it does not agree with what was determined in part f, this is because the value is nearly double that in f.


```

## h)
Do part g) again, but this time use 10000 samples.
```{r}
mydata = data.frame(ADP)
sam0 = replicate(10000,sample(mydata$ADP.Adjusted,50))
sign0 = sign(diff(sam0,log=1, differences =1))
sign0[sign0==-1] = 0
sum_0 = (colSums(sign0))
length(subset(sum_0,(24.3)>sum_0 & sum_0>(20.3)))/10000


```



