---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #2.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name:Zain ElHashemite

CWID:20010286

Date:2/4/2023




```{r}
CWID = 20010286 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}

```

# Question 1

For this question, you will need to choose two assets and download the daily adjusted close for the last (calendar) year.  Save this data as a csv and then read it in as a data frame.  You will use this data to do the following:
```{r}
#install.packages("ggplot2")

library(quantmod)
getSymbols("AAPL", src = "yahoo", from = "2022-01-01", to = "2023-01-01")
getSymbols("ADP", src = "yahoo", from = "2022-01-01", to = "2023-01-01")

write.csv(as.data.frame(AAPL), "AAPL.csv")
write.csv(as.data.frame(ADP), "ADP.csv")

frame1 = data.frame(AAPL)
frame2 = data.frame(ADP)

```

## a) 

For each of your assets, find the sample mean and sample standard deviation of your data.

```{r}
mean(AAPL$AAPL.Adjusted)
mean(ADP$ADP.Adjusted)
sd(AAPL$AAPL.Adjusted)
sd(ADP$ADP.Adjusted)
```

## b)

Create a histogram for each asset, showing each in its own plot. 

```{r}
hist(AAPL$AAPL.Adjusted, main = "AAPL Adjusted CLose")

hist(ADP$ADP.Adjusted, main = "ADP Adjusted Close")
```

## c)

Create a box-plot for each asset

```{r}
boxplot(AAPL$AAPL.Adjusted, main = "AAPL Adjusted Close", ylab = "Close Price")
boxplot(ADP$ADP.Adjusted, main = "ADP Adjusted Close", ylab = "Close Price")
```

## d)

Determine the sample covariance and sample correlation coeffecient for these two assets.

```{r}
cov(AAPL$AAPL.Adjusted,ADP$ADP.Adjusted)

cor(AAPL$AAPL.Adjusted,ADP$ADP.Adjusted)


```



# Question 2 (Adapted from Stinerock: Statistics with R)

Using the Cars93 data (which can be found in the MASS package)
## a)
Print out the variable names

```{r}
library(MASS)
names(Cars93)
```
## b)
For the Type variable, print out the frequency and relative frequency tables.  Using these tables, what percentage of the data set are large cars?

```{r}
freq = summary(Cars93$Type)
total = length(Cars93$Type)
relfreq = freq/total

freq
relfreq

#11.82% of the cars in the dataset are large cars

```
## c)
Create a cross-tabulation table of the variables Origin and Type.  Using this table, can you conclude that most of the vehicles are of US origin?

```{r}
library(gmodels)
CrossTable(Cars93$Origin,Cars93$Type)
#Yes, 48 of the cars are from the US while 45 are not from the US


```

# Question 3 (Adapted from Stinerock: Statistics with R)

Using the LakeHuron data set (already in R), find the range, interquartile range, variance, standard deviation, and coeffecient of variation.


```{r}
data("LakeHuron")
LakeHuron.range = max(LakeHuron) - min(LakeHuron) #range
LakeHuron.range

LakeHuron.iqr = IQR(LakeHuron) #interquartile Range
LakeHuron.iqr

LakeHuron.var = var(LakeHuron) #variance
LakeHuron.var

LakeHuron.sd = sd(LakeHuron) #standard deviation
LakeHuron.sd

LakeHuron.cv = sd(LakeHuron)/mean(LakeHuron) #coefficient of variation
LakeHuron.cv


```







