---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# QF112.  Homework #6.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge my honor that I have abided by the Stevens Honor System.

By filling out the following fields, you are signing this pledge.  No assignment will get credit without being pledged.

Name: Zain ElHashemite

CWID: 20010286

Date: 3/25/2023




```{r}
CWID = 20010286 #Place here your Campus wide ID number, this will personalize
#your results, but still maintain the reproduceable nature of using seeds.
#If you ever need to reset the seed in this assignment, use this as your seed
#Papers that use -1 as this CWID variable will earn 0's so make sure you change
#this value before you submit your work.
personal = CWID %% 10000
set.seed(personal)
```

It will be up to you to determine where you should use R code in this document.  You can easily add a new section of code by simply using copy/paste or typing it in yourself.  For your convenience, a blank section of code is provided below.

```{r}
# my response
```

# Question 1 

For this problem, you will be using your previous data set of the two assets that you downloaded.

```{r}
library(quantmod)
getSymbols("AAPL", src = "yahoo", from = "2022-01-01", to = "2023-01-01")
getSymbols("ADP", src = "yahoo", from = "2022-01-01", to = "2023-01-01")

write.csv(as.data.frame(AAPL), "AAPL.csv")
write.csv(as.data.frame(ADP), "ADP.csv")

frame1 = data.frame(AAPL)
frame2 = data.frame(ADP)
```

## a)

Do these assets have a net day to day increase the majority of the time?  Choose your own significance level that you feel will be relevant for this question.

```{r}
#probability that Apple will increase
change = diff(AAPL$AAPL.Adjusted)
sign = sign(change)
pAAPL = (sum(sign$AAPL.Adjusted[-1]>0))/length(sign$AAPL.Adjusted)
pAAPL
  
#probability that ADP will increase
change = diff(ADP$ADP.Adjusted)
sign = sign(change)
pADP = (sum(sign$ADP.Adjusted[-1]>0))/length(sign$ADP.Adjusted)
pADP
  
#find rejection regions, 5% siginificance level

rejectAAPL = .5+qnorm(1-.05)*sqrt((.5*(1-.5)/length(sign$AAPL.Adjusted)))
rejectAAPL

rejectADP = .5+qnorm(1-.05)*sqrt((.5*(1-.5)/length(sign$ADP.Adjusted)))
rejectADP

#We can reject AAPL's statistic as it lies outside of the region of rejection, 
#however we fail to reject ADP's statistic as it lies within its region of rejection
```

## b)

Is the standard deviation of the simple returns for each asset greater than .015?  Again choose a level of significance that you feel is relevant.

```{r}

sd_AAPL = sd(dailyReturn(AAPL$AAPL.Adjusted))
sd_ADP = sd(dailyReturn(ADP$ADP.Adjusted))

# set the significance level
alpha = 0.05

# test if the standard deviation of AAPL's daily returns is greater than 0.015
testAAPL = t.test(dailyReturn(AAPL$AAPL.Adjusted), alternative = "greater", mu = 0.015)

(testAAPL$p.value > alpha)

# test if the standard deviation of ADP's daily returns is greater than 0.015
testADP = t.test(dailyReturn(ADP$ADP.Adjusted), alternative = "greater", mu = 0.015)

(testADP$p.value > alpha)

#The standard deviation of AAPL's daily returns is not greater than 0.015 
#with a significance level of 0.05 

#The standard deviation of ADP's daily returns is not greater than 0.015 
#with a significance level of 0.05 

```

# Question 2 (Adapted from Stinerock)

Doctors in Tampa reportedly earn an average salary of 141,300 dollars.  We conduct a survey of doctors in New Orleans with a sample of size $n=64$ to test whether their mean salary is different from that in Tampa and get the result that our sample mean is 138,000 dollars.

## a)

If we assume that $\sigma=18,000$, at the level of $\alpha=.01$ use the six-step framework to test whether the true mean in New Orleans is different from that of Tampa.

```{r}
mu = 141300
n = 64
xbar = 138000
sigma = 18000
alpha = 0.01

#confidence intervals
upper = xbar+qnorm(1-alpha/2)*(sigma/sqrt(n))
upper

lower = xbar-qnorm(1-alpha/2)*(sigma/sqrt(n))
lower

CI = c(lower,upper)
CI

z = (xbar - mu)/(sigma/(sqrt(n)))
z

p = 2*(1-pnorm(abs(z)))
p

#since p is greater than alpha (0.1424668 > 0.01), we fail to 
#reject the null hypothesis

```

## b)

What is the $p$-value?

```{r}
z = (xbar-mu)/(sigma/(sqrt(n)))
z

p= 2*(1-pnorm(abs(z)))
p

#p value: 0.1424668

```

## c)

If we assume that $\sigma=18,000$, at the level of $\alpha=.01$ use the six-step framework to test whether the true mean in New Orleans is less than that of Tampa.

```{r}

#null hypothesis: the true mean salary of doctors in new orleans is the same 
#as tampa, mu = $141,300

#alternate hypothesis: the true mean salary of doctors in new orleans is less 
#than tampa, mu < $141,300

#same variables as used in above questions, except this is a one-tailed

z = (xbar-mu)/(sigma/sqrt(n))
z

p = pnorm(z)
p

#p value: 0.07123338
#fail to reject the null hypothesis as p is still greater than alpha 
#(0.07123338 > 0.01)

```

## d)

If the true mean in New Orleans is actually 139,000 dollars, what is the $\beta$ of this test?

```{r}
truemean = 139000

b= 1-pnorm(-qnorm(1-alpha)+(mu-truemean)/(sigma/sqrt(n)))
b

#beta = 0.9039046

```

# Question 3 (Adapted from Probability and Statistics for Engineers and Scientest by Walpole Myers Myers and Ye)

Based on past experiences, a professor believes that the time that it takes students to complete a test is a random variable with mean 35 minutes.  If a random sample of 20 students is taken that has a sample average time of 33.1 minutes with standard deviation 4.3, at the .05 significance level, should the professor determine that the true mean is actually less than the 35?

```{r}

mu = 35
n = 20
xbar = 33.1
sampsd = 4.3
alpha = 0.05

#null hypothesis: mu = 35
#alternate hypothesis: mu < 35

z = z = (xbar-mu)/(sampsd/sqrt(n))
z

p = pnorm(z)
p

#p value = 0.02407399

#since p is less than alpha (0.02407399 < 0.05), we can reject the null hypothesis
```


